### 2019-12-12 README.Rmd
updated vignettes and documentation
updated docs

msBalance is a an R package for analysis of balance responses in people with and without multiple sclerosis (MS).
The source data were created by Jessie Huisinga, Ph.D., and collected by Daniel Peterson, Ph.D.
The analysis code was primarily developed by J. LUcas McKay, Ph.D., M.S.C.R.

## Getting msBalance

@@

To work on the package for others to use:

1. Be sure to have `devtools` installed.
1. Use RStudio to create a local copy in `~/tmp` based on https://github.com/jlucasmckay/MSbalance
1. `devtools::check()`
1. `devtools::build_vignettes()`
1. `browseVignettes("MSbalance")`
1. Edit
1. Stage changed files, commit, and push changes with the git panel.

### Installing from GitHub for use

Currently msBalance is available on github.
It is being developed to meet CRAN requirements but is not available there at present.
To use the package yourself:

1. Be sure to have `devtools` installed.
1. Call `remove.packages("msBalance")` if you have installed the package previously.
1. `devtools::install_github("jlucasmckay/msBalance", build_vignettes = TRUE)`
1. `browseVignettes("msBalance")`

## Using msBalance

The best way to get started is by using the `msBalance` vignette.

>>>>

msBalance is a an R package for analysis of balance responses in people with and without multiple sclerosis (MS).
The source data were created by Jessie Huisinga, Ph.D., and collected by Daniel Peterson, Ph.D.
The analysis code was primarily developed by J. Lucas McKay, Ph.D., M.S.C.R.

## Getting and installing msBalance

@@

To download, develop, and install:

1. Be sure to have `devtools` installed.
1. Use RStudio to create a local copy in `~/tmp` based on https://github.com/jlucasmckay/MSbalance
1. Edit vignettes/msBalance.Rmd and R files in R/.
1. Stage changed files, commit, and push changes with the git panel.
1. `devtools::install_github("jlucasmckay/msBalance", build_vignettes = TRUE)`
1. `vignette("msBalance")`
